---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRC8WvZSWa5UAN8KPAbDuwSsBGlKWZQyvBk7BBduplsAEYLTTFgy08zMJ7ZwBUDn3JdCtHUSoghp0nE/pub?output=csv")

latest_data <- logged_data %>% 
  rename(
    media_most_time_spent_on = 2,
    minutes_today_on_media = 3,
    time_of_day = 4,
    purpose_of_media = 5
  )

time_spent_on_media <- latest_data$minutes_today_on_media

```

```{css}
body {
  font-family: Helvetica, sans-serif;
  line-height: 1.6;
  background-color: #ffffff;
  color: #222222;
  margin: 40px;
}

h1, h2, h3 {
  font-weight: 600;
  color: #2E86AB;
}

h2 {
  border-bottom: 1px solid #e0e0e0;
  padding-bottom: 5px;
}

p {
  font-size: 16px;
}

img {
  max-width: 100%;
  height: auto;
}
```

## Media Consumption Report

This report analyses media consumption patterns based on an observational log I filled out in the past two weeks.
It focuses on the time I spent on different forms of media, types of media I used, and the purpose of the media I used. 
This will provide me with insights to patterns within my media usage, which will be helpful to become monitor trends. 

--- 

### How much time are people spending on media?
```{r}
min_time <- min(time_spent_on_media, na.rm = TRUE)
max_time <- max(time_spent_on_media, na.rm = TRUE)
mean_time <- mean(time_spent_on_media, na.rm = TRUE)

ggplot(data = latest_data) +
  geom_bar(aes(x = minutes_today_on_media), fill = "#A20403") + 
  labs(
    title = "Distribution of time spent on media",
    subtitle = "Shows how many people fall into each time range (in minutes).",
    caption = "Source: Google Form Observational Log Survey",
    x = "Time spent (minutes)",
    y = "Number of people"
  )

```

The minimum time spent on media was `r min_time` minutes,
while the maximum was `r max_time` minutes.

The average (mean) time spent on media was `r mean_time` minutes.

This suggests that use of media varied significantly over a period of two weeks, where at some points I was spending not a lot of time consuming media, and others a lot more. This could be due to external factors such as university, hangouts, or events.

--- 

### What type of media is most commonly used?

```{r}
ggplot(data = latest_data) +
  geom_bar(aes(x = media_most_time_spent_on), fill = "#B40283") + 
  labs(
    title = "Most used media",
    subtitle = "Shows which media platforms are used most frequently.",
    caption = "Source: Google Form Observational Log Survey",
    x = "Media Platform",
    y = "Number of people"
  )
```

This chart shows which media platforms I used most frequently.

From the data, we can observe which platforms are most dominant in daily media consumption habits. In this bar graph we can see that I consumed TikTok and Instagram (social media) the most over the span of two weeks, with reading being the next type of media I consumed the most.

--- 

### When is media most commonly used?

```{r}
number_of_entries <- length(time_spent_on_media)

ggplot(data = latest_data) +
  geom_bar(aes(y = time_of_day), fill = "#2E86AB") + 
  labs(
    title = "Time of day media is used",
    subtitle = "Shows when people tend to use media the most during the day.",
    caption = "Source: Google Form Observational Log Survey",
    x = "Number of people",
    y = "Time of day"
  )
```

This graph shows the times of day when my media usage is highest.

It helps identify patterns in my daily behaviour, and when I am most likely to engage with media. From the graph we can infer that I spend the most time consuming media between the hours of 9pm - 6am, late night. The next most common time I consume media is the evening, between 5pm - 9pm. this suggests that I tend to consume media later during the day rather than in the early morning.

However, I only have `r number_of_entries` entries in this observational log, which is too small of a sample size to come to any statistically significant conclusion.

---

### Summary of findings

The data shows patterns in:

- How much time people spend on media
- What types of media are most popular
- When people use media
- Why people use media

Overall, this provides insight into daily media consumption habits and highlights trends in behaviour.

